\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{microtype}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black,
}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}[definition]{Example}
\newtheorem{notation}[definition]{Notation}

\theoremstyle{plain}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}

\theoremstyle{remark}
\newtheorem{remark}[definition]{Remark}

\newcommand{\Tv}{\mathbf{T}}
\newcommand{\Fv}{\mathbf{F}}
\newcommand{\Uv}{\mathbf{U}}
\newcommand{\Vals}{\{\Tv, \Fv, \Uv\}}
\newcommand{\Vh}{\widehat{V}}
\newcommand{\frm}{(l, \theta, o)}
\newcommand{\entails}{\vDash}
\newcommand{\eqv}{\equiv}
\newcommand{\Lang}{\mathcal{L}}
\newcommand{\AP}{\mathrm{AP}}
\newcommand{\Mod}{\mathcal{M}}
\newcommand{\Frame}{\mathcal{F}}

\title{Location, Time, and Observer Based Three-Valued Logic:\\
A Minimal Formal System Where Truth is Never Absolute}
\author{Norbert Nopper}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We present \textbf{LTO-K3}, a minimal formal system in which the truth value
of a proposition is never absolute but is always evaluated with respect to
three explicit parameters: a \emph{location}, a \emph{time}, and an
\emph{observer}. The system admits exactly three truth values---$\Tv$~(true),
$\Fv$~(false), and $\Uv$~(unknown)---composed via Kleene's strong
three-valued connectives. We give a formal syntax, a compositional
point-wise semantics
$\Vh : \Lang \times L \times \Theta \times O \to \Vals$,
two consequence relations (local and universal), and prove a small body of
results: uniqueness of the extended valuation, locality,
information-monotonicity, conservativity over classical logic, replacement
of equivalents, the De~Morgan laws, the absence of $\Tv$-tautologies, and a
reduction theorem that shows LTO-K3 at a fixed point is exactly Kleene's
$K_3$. From the reduction theorem we inherit decidability, the
co-NP-completeness of consequence, and the existence of sound and complete
proof systems. We are careful to distinguish what is genuinely new (the
\emph{packaging}: location and observer as non-optional, concrete
parameters; a deliberate refusal to introduce modal operators) from what is
inherited from established work~\cite{kleene1952,lukasiewicz1920,prior1957,
hintikka1962,kripke1963}. The contribution is therefore a careful synthesis
with explicit, proven properties, not a discovery, and we name its
limitations explicitly.
\end{abstract}

\noindent\textbf{Keywords:} three-valued logic, Kleene logic, indexed
semantics, temporal logic, epistemic logic, contextual semantics, partial
information.

\section{Introduction}
\label{sec:intro}

Classical two-valued logic forces every proposition into one of two states:
\emph{true} or \emph{false}. In many practical settings---verification of
distributed systems, knowledge representation, robotics, legal reasoning,
data quality---this dichotomy is too coarse. Truth often depends on
\emph{where} an evaluation is performed, \emph{when} it is performed, and
\emph{who} performs it, and in many cases the evaluator simply does not
know.

We introduce a minimal logic, \textbf{LTO-K3} (Location, Time, Observer;
Kleene three-valued), that takes these dependencies as primitive. Every
atomic proposition is evaluated under an explicit tuple
$\frm$ of location, time, and observer, and takes one of three values:
true, false, or unknown. Compound formulas are evaluated point-wise via
Kleene's strong three-valued tables.

The system is intentionally austere: no modal operators, no accessibility
relations, no transition systems, no quantification over locations, times,
or observers. Its purpose is to serve as a compact, unambiguous core on
which richer domain-specific layers may be built.

\paragraph{Contributions.}
\begin{enumerate}
  \item A formal syntax and compositional point-wise semantics for a
  three-valued indexed logic over $(L, \Theta, O)$ frames
  (Sections~\ref{sec:syntax}--\ref{sec:semantics}).
  \item A \emph{reduction theorem} (Theorem~\ref{thm:reduction}) showing
  that at every fixed point $\frm$, LTO-K3 is exactly Kleene's $K_3$,
  whence all meta-theoretic results for $K_3$ lift to LTO-K3.
  \item Two consequence relations---local at a point and universal across
  models and points---together with an explicit example separating them
  (Section~\ref{sec:consequence}).
  \item A small body of meta-theoretic results
  (Section~\ref{sec:properties}): uniqueness, locality,
  information-monotonicity, conservativity over classical logic,
  replacement of equivalents, De~Morgan laws, absence of $\Tv$-tautologies.
  \item Decidability and complexity results
  (Section~\ref{sec:complexity}): model checking is linear; local and
  universal consequence are co-NP-complete; sound and complete proof
  systems exist (inherited from $K_3$).
  \item A worked example (Section~\ref{sec:example}) and an explicit
  comparison with the closest neighbours: Kleene $K_3$,
  {\L}ukasiewicz $\text{\L}_3$, Bochvar $B_3$, Priest's LP, Belnap's
  $\mathbf{FOUR}$, hybrid logic, and multi-agent epistemic temporal logic
  (Section~\ref{sec:related}).
  \item A frank limitations section (Section~\ref{sec:limitations}).
\end{enumerate}

\paragraph{What is and is not new.}
None of the parts is new. Three-valued logics go back to
{\L}ukasiewicz~\cite{lukasiewicz1920} and Kleene~\cite{kleene1952}.
Temporal indexing goes back to Prior~\cite{prior1957}; possible-worlds
indexing to Kripke~\cite{kripke1963}; agent indexing to
Hintikka~\cite{hintikka1962} and, in computer science, to
Fagin~et~al.~\cite{fagin1995}. Sound and complete proof systems for $K_3$
(tableaux, signed-clause resolution) are well known~\cite{hahnle1993}.
What is new is the \emph{packaging}: location, time, and observer are
simultaneously non-optional, concrete, first-class parameters of a single
valuation function, and we deliberately refuse to lift them with modal
operators. The reduction theorem makes precise the sense in which our
contribution is a packaging and not a new logic.

\section{Preliminaries: Kleene's Strong Three-Valued Logic}
\label{sec:prelim}

Kleene's strong three-valued logic $K_3$~\cite{kleene1952} extends classical
two-valued logic with a third value $\Uv$ (``unknown'' / ``undefined'') and
defines the connectives so that $\Uv$ propagates conservatively: a
connective returns $\Tv$ (resp.\ $\Fv$) iff every way of resolving each
$\Uv$ to $\Tv$ or $\Fv$ would yield $\Tv$ (resp.\ $\Fv$); otherwise it
returns $\Uv$. The truth tables are:

\begin{center}
$\begin{array}{c|ccc}
\land & \Tv & \Uv & \Fv \\ \hline
\Tv & \Tv & \Uv & \Fv \\
\Uv & \Uv & \Uv & \Fv \\
\Fv & \Fv & \Fv & \Fv
\end{array}$\qquad
$\begin{array}{c|ccc}
\lor & \Tv & \Uv & \Fv \\ \hline
\Tv & \Tv & \Tv & \Tv \\
\Uv & \Tv & \Uv & \Uv \\
\Fv & \Tv & \Uv & \Fv
\end{array}$\qquad
$\begin{array}{c|c}
p & \lnot p \\ \hline
\Tv & \Fv \\
\Uv & \Uv \\
\Fv & \Tv
\end{array}$
\end{center}

We treat material implication as a defined abbreviation: $\varphi \to
\psi \;:=\; \lnot\varphi \lor \psi$. This is strong-Kleene implication;
{\L}ukasiewicz's $\text{\L}_3$ uses a different connective, where
$\Uv \to_{\text{\L}_3} \Uv = \Tv$ rather than $\Uv$ (see
Section~\ref{sec:related}). The induced truth table for $\to$ is:
\begin{center}
$\begin{array}{c|ccc}
\to & \Tv & \Uv & \Fv \\ \hline
\Tv & \Tv & \Uv & \Fv \\
\Uv & \Tv & \Uv & \Uv \\
\Fv & \Tv & \Tv & \Tv
\end{array}$
\end{center}

\paragraph{Information ordering.}
Define the partial order $\sqsubseteq$ on $\Vals$ by $\Uv \sqsubseteq \Tv$,
$\Uv \sqsubseteq \Fv$, and $x \sqsubseteq x$ for all $x$; $\Tv$ and $\Fv$
are incomparable. Intuitively, $x \sqsubseteq y$ means ``$y$ contains at
least as much information as $x$.'' All Kleene connectives are
\emph{monotone} in $\sqsubseteq$ component-wise: resolving an $\Uv$ to
$\Tv$ or $\Fv$ never reverses an already-determined value. This is the
formal reason $K_3$ is appropriate when $\Uv$ denotes epistemic
uncertainty.

\paragraph{Functional incompleteness.}
$K_3$ is not functionally complete on $\Vals$: every formula built from
$\{\lnot, \land, \lor\}$ over atoms valued $\Uv$ evaluates to $\Uv$
(immediate from the truth tables). In particular there are no constants
$\Tv, \Fv$ definable from the connectives alone. This fact underlies the
absence of $\Tv$-tautologies (Theorem~\ref{thm:notaut}).

\section{Syntax}
\label{sec:syntax}

Fix a countably infinite set $\AP$ of \emph{atomic propositions}
$p, q, r, \ldots$. The language $\Lang$ is generated by the grammar
\[
\varphi, \psi \;::=\; p \;\mid\; \lnot\varphi \;\mid\; (\varphi \land \psi)
\;\mid\; (\varphi \lor \psi),
\qquad p \in \AP.
\]
We omit parentheses under the usual precedence
$\lnot > \land > \lor$, and use $\varphi \to \psi$ as an abbreviation for
$\lnot\varphi \lor \psi$. The set of atomic propositions occurring in
$\varphi$ is written $\AP(\varphi)$.

\begin{remark}
The biconditional $\leftrightarrow$ and the quantifiers $\forall, \exists$
are deliberately omitted. The biconditional could be defined as
$(\varphi \to \psi) \land (\psi \to \varphi)$ but its $K_3$ behaviour is
non-standard and we prefer to omit it. Quantifiers would force a domain
commitment orthogonal to indexing. Crucially, $\Lang$ contains \emph{no
modal operators} indexed over $L, \Theta, O$ (no $\Box_l$, no
$\mathsf{F}\theta$, no $K_o\varphi$). This is the essential design
choice: indices appear in the meta-language, not in the object language.
\end{remark}

\section{Semantics}
\label{sec:semantics}

\subsection{Frames and models}

\begin{definition}[Frame]
A \emph{frame} is a triple $\Frame = (L, \Theta, O)$ where $L$, $\Theta$,
and $O$ are non-empty sets of \emph{locations}, \emph{times}, and
\emph{observers}, respectively. We call $\frm \in L \times \Theta \times O$
a \emph{point} of the frame.
\end{definition}

We impose no structure on $L$, $\Theta$, or $O$: $\Theta$ is not required
to be ordered, $L$ not required to carry a topology, $O$ not required to
carry an information-state relation. Any such structure is a
domain-specific extension; see Section~\ref{sec:limitations}.

\begin{definition}[Model]
An \emph{LTO-K3 model} is a pair $\Mod = (\Frame, V)$ where
$\Frame = (L, \Theta, O)$ is a frame and
\[
V : \AP \times L \times \Theta \times O \;\longrightarrow\; \Vals
\]
is a total \emph{base valuation} assigning a truth value to each atomic
proposition at each point.
\end{definition}

\subsection{Compositional valuation}

\begin{definition}[Extended valuation]
\label{def:extended}
Let $\Mod = (\Frame, V)$ be a model. The \emph{extended valuation}
$\Vh : \Lang \times L \times \Theta \times O \to \Vals$ is defined by
structural recursion on $\varphi$:
\begin{align*}
\Vh(p, l, \theta, o) &\;=\; V(p, l, \theta, o), \quad p \in \AP, \\
\Vh(\lnot\varphi, l, \theta, o) &\;=\; \lnot_{K_3} \Vh(\varphi, l, \theta, o), \\
\Vh(\varphi \land \psi, l, \theta, o) &\;=\; \Vh(\varphi, l, \theta, o)
                                              \land_{K_3} \Vh(\psi, l, \theta, o), \\
\Vh(\varphi \lor \psi, l, \theta, o) &\;=\; \Vh(\varphi, l, \theta, o)
                                              \lor_{K_3} \Vh(\psi, l, \theta, o),
\end{align*}
where $\lnot_{K_3}, \land_{K_3}, \lor_{K_3}$ are the Kleene connectives of
Section~\ref{sec:prelim}.
\end{definition}

\begin{proposition}[Existence and uniqueness of $\Vh$]
\label{prop:unique}
For every model $\Mod$, the function $\Vh$ defined in
Definition~\ref{def:extended} exists and is unique.
\end{proposition}

\begin{proof}
$\Lang$ is the absolutely free algebra on $\AP$ over the signature
$\{\lnot, \land, \lor\}$ (with arities $1, 2, 2$). At each fixed point
$\frm$, $(\Vals, \lnot_{K_3}, \land_{K_3}, \lor_{K_3})$ is an algebra of
the same signature. The map $p \mapsto V(p, l, \theta, o)$ on generators
extends, by the universal property of free algebras, to a unique
homomorphism $\Vh(-, l, \theta, o) : \Lang \to \Vals$. Doing this at every
point yields $\Vh$.
\end{proof}

Crucially, the recursion is \emph{point-wise}: both sides of every binary
connective are evaluated at \emph{the same} point. There is no syntactic
mechanism in $\Lang$ for referring to a different point.

\begin{remark}[On cross-frame composition]
$\Lang$ contains no formula whose two sub-formulas can be evaluated at
different points; Definition~\ref{def:extended} forces a single $\frm$
throughout. Defining cross-frame operators would require explicit
bridging rules (synchronization, trust, observer alignment) that are
domain-specific. Such extensions are outside the core system; see
Section~\ref{sec:limitations}.
\end{remark}

\section{Reduction to Pointwise $K_3$}
\label{sec:reduction}

This section formalises the sense in which LTO-K3 is, at every fixed
point, exactly Kleene's $K_3$. The reduction theorem is the central
meta-fact of the paper: it lets us inherit completeness, decidability, and
proof systems from $K_3$ without re-proving them.

\begin{definition}[Point restriction]
Let $\Mod = (\Frame, V)$ be a model and $\frm$ a point. The
\emph{$K_3$-assignment induced at $\frm$} is the function
$v_{\frm}^{\Mod} : \AP \to \Vals$ defined by
$v_{\frm}^{\Mod}(p) = V(p, l, \theta, o)$.
\end{definition}

Let $\Vh_{K_3} : \Lang \times (\AP \to \Vals) \to \Vals$ denote the
standard $K_3$ semantics: $\Vh_{K_3}(\varphi, v)$ is the value of
$\varphi$ under the assignment $v$ using the Kleene tables.

\begin{theorem}[Reduction]
\label{thm:reduction}
For every model $\Mod$, every formula $\varphi \in \Lang$, and every point
$\frm$,
\[
\Vh(\varphi, l, \theta, o) \;=\; \Vh_{K_3}\bigl(\varphi,\, v_{\frm}^{\Mod}\bigr).
\]
\end{theorem}

\begin{proof}
Structural induction on $\varphi$. Base: for $p \in \AP$ both sides equal
$V(p, l, \theta, o)$. Step: each compound case applies exactly the same
Kleene connective on either side, and the induction hypothesis equates
the sub-formula values. \qedhere
\end{proof}

\begin{corollary}[Inheritance from $K_3$]
\label{cor:inherit}
Every property of $K_3$ formulated in terms of a single assignment lifts
point-wise to LTO-K3. In particular, the propositional fragment of LTO-K3
inherits from $K_3$:
\begin{enumerate}
  \item the absence of $\Tv$-tautologies (Theorem~\ref{thm:notaut} below),
  \item the existence of sound and complete proof systems
  (tableaux, signed-clause resolution)~\cite{hahnle1993},
  \item the co-NP-completeness of consequence (Section~\ref{sec:complexity}).
\end{enumerate}
\end{corollary}

\section{Consequence Relations}
\label{sec:consequence}

We take $\Tv$ as the sole designated value. (Designating $\{\Tv, \Uv\}$
gives Priest's LP~\cite{priest1979}, a different logic.)

\begin{definition}[Local satisfaction]
Let $\Mod = (\Frame, V)$ be a model and $\frm$ a point. We say
$\varphi$ is \emph{satisfied at $\frm$ in $\Mod$}, written
$\Mod, \frm \entails \varphi$, iff
$\Vh(\varphi, l, \theta, o) = \Tv$.
\end{definition}

\begin{definition}[Consequence]
Let $\Gamma \subseteq \Lang$ and $\varphi \in \Lang$.
\begin{itemize}
  \item \emph{Local entailment at $\frm$ in $\Mod$}, written
  $\Gamma \entails_{\Mod, \frm} \varphi$: if every $\gamma \in \Gamma$
  satisfies $\Mod, \frm \entails \gamma$, then $\Mod, \frm \entails \varphi$.
  \item \emph{Universal entailment} $\Gamma \entails \varphi$:
  $\Gamma \entails_{\Mod, \frm} \varphi$ for every model $\Mod$ and every
  point $\frm$ of $\Mod$.
\end{itemize}
\end{definition}

\begin{proposition}[Universal entails local]
$\Gamma \entails \varphi$ implies
$\Gamma \entails_{\Mod, \frm} \varphi$ for every $\Mod$ and $\frm$. The
converse fails.
\end{proposition}

\begin{proof}
The forward direction is immediate from the definition. For failure of
the converse, take any frame with two points $\frm_1 \neq \frm_2$, an atom
$p \in \AP$, and the model $V$ defined by $V(p, \frm_1) = \Tv$,
$V(p, \frm_2) = \Fv$, and $V(q, \cdot) = \Uv$ for every other atom $q$
and every point. Then $\varnothing \entails_{\Mod, \frm_1} p$ (since
$\Mod, \frm_1 \entails p$) but $\varnothing \not\entails p$
(Theorem~\ref{thm:notaut}).
\end{proof}

\begin{remark}
By Theorem~\ref{thm:reduction}, universal entailment coincides with
$K_3$-consequence at the level of formulas: $\Gamma \entails \varphi$ iff
for every $K_3$-assignment $v : \AP \to \Vals$, if $\Vh_{K_3}(\gamma, v)
= \Tv$ for every $\gamma \in \Gamma$ then $\Vh_{K_3}(\varphi, v) = \Tv$.
Indexing adds nothing at the universal level; it matters only locally.
\end{remark}

\section{Properties}
\label{sec:properties}

We collect the basic meta-theoretic properties of LTO-K3. Most are
immediate corollaries of Theorem~\ref{thm:reduction}; we state them for
completeness and to fix notation for the indexed setting.

\begin{lemma}[Locality]\label{lem:locality}
For every model $\Mod$, every formula $\varphi$, and every point $\frm$,
$\Vh(\varphi, l, \theta, o)$ depends only on the restriction of $V$ to
$\AP(\varphi) \times \{l\} \times \{\theta\} \times \{o\}$.
\end{lemma}

\begin{proof}
By Theorem~\ref{thm:reduction}, $\Vh(\varphi, l, \theta, o) =
\Vh_{K_3}(\varphi, v_{\frm}^{\Mod})$, and standard $K_3$-semantics
depends only on the values of $v_{\frm}^{\Mod}$ on $\AP(\varphi)$.
\end{proof}

\begin{proposition}[Information-monotonicity]\label{prop:mono}
Let $V_1, V_2$ be base valuations on the same frame with
$V_1(p, l, \theta, o) \sqsubseteq V_2(p, l, \theta, o)$ for every atom
and every point. Then for every formula $\varphi$ and every point $\frm$,
$\Vh_1(\varphi, l, \theta, o) \sqsubseteq \Vh_2(\varphi, l, \theta, o)$.
\end{proposition}

\begin{proof}
At a fixed $\frm$, both sides equal the $K_3$-evaluation of $\varphi$
under the induced assignments, and $\lnot_{K_3}, \land_{K_3}, \lor_{K_3}$
are monotone in $\sqsubseteq$ component-wise (standard $K_3$ result,
verified by inspection of the truth tables). Structural induction
completes the proof.
\end{proof}

\begin{corollary}[Conservativity over classical logic]\label{cor:cons}
Let $\Mod$ be a model in which $V$ never takes the value $\Uv$. Then for
every formula $\varphi$ and every point $\frm$,
$\Vh(\varphi, l, \theta, o) \in \{\Tv, \Fv\}$, and the resulting value
coincides with the classical (two-valued) valuation of $\varphi$ under
the same atomic assignment.
\end{corollary}

\begin{proof}
When neither input is $\Uv$, every Kleene connective returns the
classical value (inspection). The corollary follows by structural
induction (alternatively, by Theorem~\ref{thm:reduction} and the
analogous $K_3$ result).
\end{proof}

\begin{notation}[Semantic equivalence]
Write $\varphi \eqv \psi$ iff $\Vh(\varphi, l, \theta, o) =
\Vh(\psi, l, \theta, o)$ for every model $\Mod$ and every point $\frm$.
\end{notation}

\begin{lemma}[Replacement of equivalents]
\label{lem:replace}
If $\varphi \eqv \psi$ then for every formula $\chi$ and every occurrence
of $\varphi$ in $\chi$, replacing that occurrence by $\psi$ yields a
formula $\chi'$ with $\chi \eqv \chi'$.
\end{lemma}

\begin{proof}
Structural induction on $\chi$. The base case ($\chi = \varphi$) is by
hypothesis. The compound cases follow because each Kleene connective is
a function of the truth values of its sub-formulas: replacing a
sub-formula by an equivalent one does not change those values, so the
top-level value is unchanged. (Equivalently: $\eqv$ is a congruence on
the formula algebra because Kleene connectives are well-defined
functions on $\Vals$.)
\end{proof}

\begin{proposition}[De Morgan laws]\label{prop:demorgan}
For all $\varphi, \psi$:
$\lnot(\varphi \land \psi) \eqv \lnot\varphi \lor \lnot\psi$ and
$\lnot(\varphi \lor \psi) \eqv \lnot\varphi \land \lnot\psi$.
\end{proposition}

\begin{proof}
At a fixed point, by case analysis on
$(\Vh(\varphi), \Vh(\psi)) \in \Vals \times \Vals$ (nine cases per
identity) using the Kleene tables.
\end{proof}

\begin{proposition}[Standard identities]\label{prop:basic}
For all $\varphi, \psi, \chi$:
$\lnot\lnot\varphi \eqv \varphi$;\;
$\varphi \land \varphi \eqv \varphi$;\;
$\varphi \lor \varphi \eqv \varphi$;\;
$\varphi \land \psi \eqv \psi \land \varphi$;\;
$\varphi \lor \psi \eqv \psi \lor \varphi$;\;
$(\varphi \land \psi) \land \chi \eqv \varphi \land (\psi \land \chi)$;\;
$(\varphi \lor \psi) \lor \chi \eqv \varphi \lor (\psi \lor \chi)$;\;
$\varphi \land (\psi \lor \chi) \eqv (\varphi \land \psi) \lor (\varphi \land \chi)$;\;
$\varphi \lor (\psi \land \chi) \eqv (\varphi \lor \psi) \land (\varphi \lor \chi)$.
\end{proposition}

\begin{proof}
Each is a finite truth-table check on $\Vals$, lifted point-wise via
Theorem~\ref{thm:reduction}.
\end{proof}

\begin{theorem}[No universal $\Tv$-tautologies]\label{thm:notaut}
There is no formula $\varphi \in \Lang$ with $\entails \varphi$.
\end{theorem}

\begin{proof}
Consider the model $\Mod_\Uv$ on any frame with $V(p, \frm) = \Uv$ for
every atom and every point. By structural induction on $\varphi$, using
that every Kleene connective returns $\Uv$ when every input is $\Uv$, we
have $\Vh(\varphi, \frm) = \Uv$ for every $\varphi$ and every $\frm$.
Hence no formula evaluates to $\Tv$ universally.
\end{proof}

\begin{corollary}\label{cor:lem}
$\not\entails p \lor \lnot p$ and $\not\entails \lnot(p \land \lnot p)$.
\end{corollary}

\begin{remark}
Theorem~\ref{thm:notaut} is the price of taking $\Tv$ as the sole
designated value in $K_3$. It does not mean the logic is useless: valid
\emph{inferences} from non-empty contexts are the appropriate notion of
validity. For example, $\{p, \lnot p \lor q\} \entails q$ holds: at any
point where $\Vh(p) = \Tv$, the table for $\lor$ forces
$\Vh(\lnot p \lor q) = \Vh(q)$, so if the latter is $\Tv$ then so is the
former.
\end{remark}

\section{Decidability and Complexity}
\label{sec:complexity}

We assume formulas, finite subsets of $\Gamma \subseteq \Lang$, finite
fragments of frames, and base valuations to be presented in the usual
finitary way (formulas as syntax trees; valuations as finite tables on
the atoms and points actually mentioned). Sizes refer to the total
description length.

\begin{proposition}[Model checking]
\label{prop:mc}
Given a finite model $\Mod$ (i.e., a finite table for $V$ on the points
and atoms used) and a formula $\varphi$, computing
$\Vh(\varphi, \frm)$ takes time $O(|\varphi|)$ assuming constant-time
lookup of $V$ at the relevant atoms.
\end{proposition}

\begin{proof}
Bottom-up evaluation of the syntax tree of $\varphi$, applying a
constant-time Kleene table lookup at each internal node.
\end{proof}

\begin{theorem}[Complexity of consequence]
\label{thm:complexity}
Universal entailment $\Gamma \entails \varphi$ for finite $\Gamma$ is
co-NP-complete. So is local entailment for finite $\Gamma$.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:reduction}, universal entailment coincides with
$K_3$-consequence at the level of formulas, which is known to be
co-NP-complete (it reduces to classical SAT/VAL via the standard
embedding of $K_3$ into classical two-valued logic; see, e.g.,
\cite{hahnle1993}). Local entailment at a specified point is at least as
hard (universal entailment is the intersection over points), and is in
co-NP by guessing a falsifying assignment at the point and checking in
linear time (Proposition~\ref{prop:mc}). Membership and hardness match,
giving co-NP-completeness.
\end{proof}

\begin{corollary}[Sound and complete proof systems]
LTO-K3 inherits, via Theorem~\ref{thm:reduction}, the sound and complete
tableau and signed-clause-resolution proof systems for
$K_3$~\cite{hahnle1993}. A formal derivation of
$\Gamma \entails \varphi$ in LTO-K3 is a $K_3$-derivation of
$\varphi$ from $\Gamma$ at the level of formulas.
\end{corollary}

\section{Worked Example}
\label{sec:example}

Let $L = \{l_{\mathrm{EU}}, l_{\mathrm{US}}\}$, $\Theta = \{\theta_0,
\theta_1\}$, $O = \{o_{\mathrm{Alice}}, o_{\mathrm{Bob}}\}$. Let $p$
abbreviate ``the package has been delivered'' and $q$ ``the package has
cleared customs.'' A base valuation:

\begin{center}
\small
\begin{tabular}{lll|cc}
\toprule
$l$ & $\theta$ & $o$ & $V(p)$ & $V(q)$ \\
\midrule
$l_{\mathrm{EU}}$ & $\theta_0$ & $o_{\mathrm{Alice}}$ & $\Uv$ & $\Fv$ \\
$l_{\mathrm{EU}}$ & $\theta_1$ & $o_{\mathrm{Alice}}$ & $\Tv$ & $\Tv$ \\
$l_{\mathrm{EU}}$ & $\theta_1$ & $o_{\mathrm{Bob}}$   & $\Uv$ & $\Tv$ \\
$l_{\mathrm{US}}$ & $\theta_1$ & $o_{\mathrm{Alice}}$ & $\Fv$ & $\Uv$ \\
\bottomrule
\end{tabular}
\end{center}

Then $\Vh(p \land q)$ takes value $\Tv$ at
$(l_{\mathrm{EU}}, \theta_1, o_{\mathrm{Alice}})$ (Alice in the EU at
$\theta_1$ knows both); $\Uv$ at $(l_{\mathrm{EU}}, \theta_1,
o_{\mathrm{Bob}})$ (Bob does not yet know whether the package has been
delivered, even though he knows it has cleared customs); and $\Fv$ at
$(l_{\mathrm{US}}, \theta_1, o_{\mathrm{Alice}})$ (the proposition is
false in the US frame because $\Vh(p) = \Fv$ there). The same formula
yields different values at different points: this is the design.

By Theorem~\ref{thm:reduction}, each row of the table determines a
$K_3$-assignment, and the value of $p \land q$ at that row is exactly the
$K_3$-evaluation of $p \land q$ under that assignment.

\section{Related Work}
\label{sec:related}

\paragraph{Three-valued logics.}
$K_3$~\cite{kleene1952} is one of several three-valued logics with
different motivations and connectives. {\L}ukasiewicz
$\text{\L}_3$~\cite{lukasiewicz1920} differs from $K_3$ only in
implication: $\Uv \to_{\text{\L}_3} \Uv = \Tv$, yielding the tautology
$p \to p$ and other classical theorems. Bochvar's internal
$B_3$~\cite{bochvar1981} is ``infectious'': any operation with a $\Uv$
input returns $\Uv$, even $\Tv \lor \Uv$. Priest's
LP~\cite{priest1979} uses the Kleene tables but designates
$\{\Tv, \Uv\}$, yielding a paraconsistent logic in which contradictions
can be true and LEM holds. Belnap's $\mathbf{FOUR}$~\cite{belnap1977}
adds a fourth value (``both true and false'') for tolerating
contradictory information.

We choose $K_3$ with designated value $\Tv$ because the reading of $\Uv$
we want is purely epistemic (``not yet known'') and information-monotonic
(Proposition~\ref{prop:mono}). $\text{\L}_3$ breaks this property
(implication is not monotone in the obvious sense); LP changes the
designated set; $B_3$ propagates $\Uv$ too aggressively; $\mathbf{FOUR}$
conflates uncertainty with inconsistency.

\paragraph{Temporal and modal logics.}
Prior~\cite{prior1957} introduced tense operators; Pnueli~\cite{pnueli1977}
introduced LTL; Clarke and Emerson~\cite{clarke1981} introduced CTL. These
logics index truth by time (or states reachable in time) but use
classical two-valued semantics and quantify over states with modal
operators. Kripke~\cite{kripke1963} gave possible-worlds semantics; the
entire modal-logic tradition~\cite{blackburn2001} indexes truth by worlds
and uses $\Box, \Diamond$ to quantify over them. Hybrid
logic~\cite{areces2007hybrid} adds nominals $i$ and $@_i$ to refer to
specific worlds in the object language. LTO-K3 differs in not
quantifying over points in the object language at all.

\paragraph{Epistemic logics.} Hintikka~\cite{hintikka1962} introduced
epistemic modal logic with $K_a$ operators; see Fagin et
al.~\cite{fagin1995} for the textbook treatment. Multi-agent epistemic
temporal logic combines these dimensions, but again with two-valued
semantics and modal operators.

\paragraph{Three-valued spatio-temporal and runtime-verification logics.}
Bauer et al.~\cite{bauer2011rv} developed LTL$_3$, a three-valued LTL
variant for runtime monitoring. Spatial logics~\cite{aiello2007handbook}
introduce explicit spatial indices for reasoning about topological
structure. These works are the closest neighbours of LTO-K3.

\paragraph{Honest positioning.} Relative to the above, LTO-K3 is
deliberately less expressive: it has fewer resources than hybrid logic,
fewer than multi-modal epistemic temporal logic, and fewer than
LTL$_3$. What it offers in return is a uniform treatment of three indices
(location, time, observer) as concrete and equally first-class, and a
self-contained semantics that fits on a page. Theorem~\ref{thm:reduction}
makes precise the price of this minimalism: at any single point, LTO-K3
is exactly $K_3$ and nothing more. We make no claim that LTO-K3
supersedes any of these systems; we claim only that it is a useful
\emph{starting point}.

\section{Limitations}
\label{sec:limitations}

\begin{enumerate}
  \item \textbf{No cross-frame operators.} LTO-K3 cannot express
  ``$\varphi$ at $l_1$ implies $\psi$ at $l_2$'' or ``$\varphi$ now will
  be $\psi$ later.''
  \item \textbf{No quantification.} LTO-K3 cannot express ``$\varphi$
  holds for some observer'' or ``$\varphi$ holds at all times.''
  \item \textbf{Structure on $L, \Theta, O$ is invisible.} Time is not
  ordered, locations are not topologized, observers do not have
  information-state relations. Such structure must be added by extension.
  \item \textbf{Functional incompleteness and no $\Tv$-tautologies.}
  Inherited from $K_3$ (Section~\ref{sec:prelim},
  Theorem~\ref{thm:notaut}). Users accustomed to tautological reasoning
  must adjust to entailment-based reasoning from non-empty contexts.
  \item \textbf{$\Uv$ is undifferentiated.} ``Not yet known,'' ``in
  principle unknowable,'' and ``not yet defined'' collapse into one
  value. Distinguishing them requires a richer truth-value
  set~\cite{belnap1977} or a probabilistic / possibilistic layer.
  \item \textbf{No interaction between observers.} There is no notion of
  ``$o_1$ knows that $o_2$ knows $\varphi$''; that requires explicit
  $K_o$ operators (out of scope).
  \item \textbf{Cross-frame undefinedness is a restriction.} We have
  framed it as a deliberate design choice, and it is, but it is also a
  real expressive limitation. Users who need cross-frame reasoning will
  need to layer on additional machinery.
  \item \textbf{No gain over $K_3$ at a fixed point.} By
  Theorem~\ref{thm:reduction}, the indexing contributes nothing at a
  single point. The value of LTO-K3 is therefore not deeper logic but
  uniform treatment of context across points and a discipline that
  forbids silent context-mixing.
\end{enumerate}

\section{Conclusion}
We have presented LTO-K3, a minimal three-valued logic in which every
proposition is evaluated under an explicit triple of location, time, and
observer. We gave a formal syntax, a compositional point-wise semantics,
two consequence relations, a reduction theorem that anchors LTO-K3 in
Kleene's $K_3$, and a small body of meta-theoretic results (uniqueness,
locality, monotonicity, conservativity, replacement, De~Morgan, absence
of $\Tv$-tautologies). The reduction theorem lets us inherit decidability,
the co-NP-completeness of consequence, and sound and complete proof
systems from $K_3$. We were explicit about what is new (the packaging)
and what is not (everything else), and named the system's limitations.
Cross-frame composition, quantification, and modal operators are
deliberate omissions to be addressed by domain-specific extensions.

\begin{thebibliography}{99}

\bibitem{lukasiewicz1920}
J.~{\L}ukasiewicz, ``O logice tr\'ojwarto\'sciowej'' [On three-valued
logic], \emph{Ruch Filozoficzny}, vol.~5, pp.~169--171, 1920.

\bibitem{kleene1952}
S.~C. Kleene, \emph{Introduction to Metamathematics}, North-Holland,
Amsterdam, 1952.

\bibitem{prior1957}
A.~N. Prior, \emph{Time and Modality}, Oxford University Press, Oxford,
1957.

\bibitem{hintikka1962}
J.~Hintikka, \emph{Knowledge and Belief: An Introduction to the Logic of
the Two Notions}, Cornell University Press, Ithaca, NY, 1962.

\bibitem{kripke1963}
S.~A. Kripke, ``Semantical considerations on modal logic,''
\emph{Acta Philosophica Fennica}, vol.~16, pp.~83--94, 1963.

\bibitem{belnap1977}
N.~D. Belnap, ``A useful four-valued logic,'' in J.~M. Dunn and
G.~Epstein, eds., \emph{Modern Uses of Multiple-Valued Logic}, Reidel,
Dordrecht, pp.~5--37, 1977.

\bibitem{pnueli1977}
A.~Pnueli, ``The temporal logic of programs,'' in \emph{Proc.\ 18th
Annual Symposium on Foundations of Computer Science (FOCS)}, IEEE,
pp.~46--57, 1977.

\bibitem{priest1979}
G.~Priest, ``The logic of paradox,'' \emph{Journal of Philosophical
Logic}, vol.~8, no.~1, pp.~219--241, 1979.

\bibitem{bochvar1981}
D.~A. Bochvar, ``On a three-valued logical calculus and its application
to the analysis of the paradoxes of the classical extended functional
calculus,'' translated by M.~Bergmann, \emph{History and Philosophy of
Logic}, vol.~2, pp.~87--112, 1981 (original Russian 1938).

\bibitem{clarke1981}
E.~M. Clarke and E.~A. Emerson, ``Design and synthesis of synchronization
skeletons using branching-time temporal logic,'' in \emph{Logics of
Programs}, LNCS 131, Springer, pp.~52--71, 1981.

\bibitem{hahnle1993}
R.~H{\"a}hnle, \emph{Automated Deduction in Multiple-Valued Logics},
Oxford University Press, Oxford, 1993.

\bibitem{fagin1995}
R.~Fagin, J.~Y. Halpern, Y.~Moses, and M.~Y. Vardi, \emph{Reasoning About
Knowledge}, MIT Press, Cambridge, MA, 1995.

\bibitem{blackburn2001}
P.~Blackburn, M.~de~Rijke, and Y.~Venema, \emph{Modal Logic}, Cambridge
University Press, Cambridge, 2001.

\bibitem{aiello2007handbook}
M.~Aiello, I.~Pratt-Hartmann, and J.~van~Benthem, eds., \emph{Handbook of
Spatial Logics}, Springer, Dordrecht, 2007.

\bibitem{areces2007hybrid}
C.~Areces and B.~ten~Cate, ``Hybrid logics,'' in P.~Blackburn,
J.~van~Benthem, and F.~Wolter, eds., \emph{Handbook of Modal Logic},
Elsevier, pp.~821--868, 2007.

\bibitem{bauer2011rv}
A.~Bauer, M.~Leucker, and C.~Schallhart, ``Runtime verification for LTL
and TLTL,'' \emph{ACM Transactions on Software Engineering and
Methodology}, vol.~20, no.~4, art.~14, 2011.

\end{thebibliography}

\end{document}
