\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{microtype}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black,
}

\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\title{Location, Time, and Observer Based Three-Valued Logic:\\
A Minimal Formal System Where Truth is Never Absolute}
\author{Norbert Nopper}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We present a minimal formal system in which the truth value of a proposition
is never absolute, but is always evaluated with respect to three explicit
parameters: a \emph{location}, a \emph{time}, and an \emph{observer}.
The system admits exactly three truth values---\textbf{T}~(true),
\textbf{F}~(false), and \textbf{U}~(unknown)---composed via Kleene's strong
three-valued connectives. Although three-valued logics, temporal logics,
epistemic logics, and modal logics have all been studied extensively, the
present contribution is not the discovery of new components but a
\emph{packaging} of known ideas into a single, minimal, self-contained primitive
$V : P \times L \times \Theta \times O \to \{T, F, U\}$, in which location and
observer are concrete and non-optional, and in which logical connectives are
explicitly undefined across distinct $(l, \theta, o)$ frames. The result is a
unified framework suitable as a starting point for systems that must reason
about partial knowledge under spatial, temporal, and epistemic context.
\end{abstract}

\noindent\textbf{Keywords:} three-valued logic, temporal logic, epistemic logic,
Kleene logic, contextual semantics.

\section{Introduction}
Classical two-valued logic forces every proposition into one of two states:
\emph{true} or \emph{false}. In many practical settings---verification,
distributed systems, knowledge representation, robotics, legal reasoning---this
dichotomy is too coarse. Truth often depends on \emph{where} an evaluation is
performed, \emph{when} it is performed, and \emph{who} performs it.

We introduce a minimal logic that takes these dependencies as primitive.
Every proposition is evaluated under an explicit tuple
$(l, \theta, o)$ of location, time, and observer, and may take one of three
values: true, false, or unknown. The system is intentionally austere: it
contains no modal operators, no accessibility relations, and no transition
systems. Its purpose is to serve as a compact, unambiguous core on which richer
domain-specific layers (synchronization, trust, frame alignment) may later be
built.

\section{Truth Values}
The system recognizes exactly three truth states, summarized in
Table~\ref{tab:values}.

\begin{table}[h]
\centering
\caption{The three truth values.}
\label{tab:values}
\begin{tabular}{ll}
\toprule
\textbf{Value} & \textbf{Meaning} \\
\midrule
\textbf{T} (True)    & Known to hold at this location, time, and for this observer. \\
\textbf{F} (False)   & Known not to hold at this location, time, and for this observer. \\
\textbf{U} (Unknown) & Indeterminate at this location, time, and for this observer. \\
\bottomrule
\end{tabular}
\end{table}

Classical logic forces every proposition into \textbf{T} or \textbf{F}. The
present system acknowledges a third reality: that we do not always know.

\section{Contextual Parameters}

\subsection{Location}
Truth is a function of \emph{where} it is evaluated. The same proposition at
the same moment can hold different values in different locations:
\begin{align*}
V(p, l_1, \theta, o) &= T \qquad \text{true in this location,} \\
V(p, l_2, \theta, o) &= F \qquad \text{false in another,} \\
V(p, l_3, \theta, o) &= U \qquad \text{unknown elsewhere.}
\end{align*}
``Location'' is broadly defined: a physical place, a network, a jurisdiction,
or a frame of reference. The essential point is that spatial and structural
context matters.

\subsection{Time}
Truth is a function of \emph{when} it is evaluated. The same proposition can
yield different values at different moments---and this is not a contradiction,
it is the system working as designed:
\begin{align*}
V(p, l, \theta_1, o) &= U \qquad \text{not yet determined,} \\
V(p, l, \theta_2, o) &= T \qquad \text{resolved to true,} \\
V(p, l, \theta_3, o) &= F \qquad \text{later becomes false.}
\end{align*}
A future event is \emph{unknown} before it occurs, \emph{true} when it
happens, and may become \emph{false} if conditions change. Time is not
optional: it is fundamental to every evaluation.

\subsection{Observer}
Truth is a function of \emph{who} evaluates it. The same proposition at the
same location and time can hold different values for different observers:
\begin{align*}
V(p, l, \theta, o_1) &= T \qquad \text{true for this observer,} \\
V(p, l, \theta, o_2) &= F \qquad \text{false for another,} \\
V(p, l, \theta, o_3) &= U \qquad \text{unknown to a third.}
\end{align*}
``Observer'' is broadly defined: a person, a sensor, a system, an institution,
or any evaluating entity. Different observers may have different information,
beliefs, or interpretive frameworks, and therefore arrive at different truth
values for the same proposition at the same location and time. This reflects
the epistemic reality that knowledge is observer-dependent.

\section{The Valuation Function}
The core primitive maps a proposition, evaluated at a location, time, and for
an observer, to a truth value.

\begin{definition}[Valuation]
Let $P$ be a set of propositions, $L$ a set of locations, $\Theta$ a set of
time points, and $O$ a set of observers. The valuation function is
\[
V : P \times L \times \Theta \times O \;\longrightarrow\; \{T, F, U\}.
\]
For any $p \in P$, $l \in L$, $\theta \in \Theta$, and $o \in O$,
\[
V(p, l, \theta, o) \in \{T, F, U\}.
\]
\end{definition}

Location, time, and observer are the \emph{inputs}; the truth value is the
\emph{output}. No parameter is optional.

\section{Logical Connectives}
The three values compose through Kleene's strong three-valued
operations~\cite{kleene1952}.

\subsection{Conjunction}
\[
\begin{array}{c|ccc}
\land & T & U & F \\ \hline
T & T & U & F \\
U & U & U & F \\
F & F & F & F
\end{array}
\]

\subsection{Disjunction}
\[
\begin{array}{c|ccc}
\lor & T & U & F \\ \hline
T & T & T & T \\
U & T & U & U \\
F & T & U & F
\end{array}
\]

\subsection{Negation}
\[
\begin{array}{c|c}
p & \lnot p \\ \hline
T & F \\
U & U \\
F & T
\end{array}
\]

\subsection{Implication}
\[
\begin{array}{c|ccc}
\to & T & U & F \\ \hline
T & T & U & F \\
U & T & U & U \\
F & T & T & T
\end{array}
\]

\subsection{Frame Discipline}
All operations are evaluated at a given $(l, \theta, o)$. When combining
propositions, both must be evaluated within the same frame:
\begin{align*}
V(p_1, l, \theta, o) \land V(p_2, l, \theta, o) &\quad \text{valid: same } (l, \theta, o), \\
V(p_1, l_1, \theta_1, o_1) \land V(p_2, l_2, \theta_2, o_2) &\quad \text{undefined: cross-frame composition.}
\end{align*}
The logical connectives never escape the location, temporal, and observer
frame.

\begin{remark}
Biconditional ($\leftrightarrow$) and quantifiers ($\forall$, $\exists$) are
deliberately omitted to keep the system minimal. They can be defined in terms
of the primitives above if needed.
\end{remark}

\begin{remark}
Cross-frame composition---combining values from different
$(l, \theta, o)$ tuples---is left undefined by design. Defining it would
require explicit bridging rules (synchronization constraints, trust policies,
observer-alignment or frame-alignment functions) that are domain-specific and
beyond the scope of this core system.
\end{remark}

\section{Novelty and Related Work}
The individual components of this system are well-established. Three-valued
logics due to {\L}ukasiewicz~\cite{lukasiewicz1920} and
Kleene~\cite{kleene1952} define truth values without temporal or spatial
indexing. Temporal logics such as LTL and CTL index truth by time but rest on
classical two-valued semantics. Epistemic logics~\cite{hintikka1962} index
truth by agent knowledge but typically remain two-valued. Modal
logics~\cite{kripke1963} index truth by possible worlds, again typically
two-valued. Three-valued spatio-temporal logics have been explored in
verification and robotics contexts.

The contribution of the present system is in its \emph{formulation}, not in
the discovery of its parts:
\begin{enumerate}
  \item \textbf{Location as concrete and non-optional.} Not abstract
  ``possible worlds'' or ``states'', but a first-class parameter representing
  physical places, networks, jurisdictions, or frames of reference.
  \item \textbf{Observer as explicit and non-optional.} Truth is always
  relative to an evaluating entity, making the epistemic dimension a
  first-class parameter rather than an implicit assumption.
  \item \textbf{The cross-frame constraint.} Logical connectives are
  explicitly undefined across different $(l, \theta, o)$ tuples, rather than
  silently mixing contexts.
  \item \textbf{Minimalism.} No modal operators ($\Box$, $\Diamond$), no
  accessibility relations, no transition systems. Just
  $V : P \times L \times \Theta \times O \to \{T, F, U\}$ as a self-contained
  primitive.
\end{enumerate}

This is a novel \emph{packaging} of known ideas into a minimal, unified formal
system---not a novel discovery.

\section{Conclusion}
We have presented a minimal three-valued logic in which every proposition is
evaluated under an explicit triple of location, time, and observer. The
resulting system is small enough to be specified on a single page, yet
expressive enough to capture partial knowledge under spatial, temporal, and
epistemic context. Cross-frame composition is intentionally left to future,
domain-specific extensions.

\begin{thebibliography}{9}
\bibitem{lukasiewicz1920}
J.~{\L}ukasiewicz, \emph{O logice tr\'ojwarto\'sciowej} [On three-valued
logic], Ruch Filozoficzny, vol.~5, pp.~170--171, 1920.

\bibitem{kleene1952}
S.~C. Kleene, \emph{Introduction to Metamathematics}, North-Holland, 1952.

\bibitem{prior1957}
A.~N. Prior, \emph{Time and Modality}, Oxford University Press, 1957.

\bibitem{hintikka1962}
J.~Hintikka, \emph{Knowledge and Belief: An Introduction to the Logic of the
Two Notions}, Cornell University Press, 1962.

\bibitem{kripke1963}
S.~A. Kripke, ``Semantical considerations on modal logic,''
\emph{Acta Philosophica Fennica}, vol.~16, pp.~83--94, 1963.
\end{thebibliography}

\end{document}
